ShrinkNets: Learning Network Size while Training

### 2018-02-09 paper/ICML/evaluation.tex

The goal of our evaluation is to explore (1) whether, by varying $\lambda$, \shrink can efficiently
explore (in terms of number of training runs)  the spectrum of high-accuracy
models from small to large, on both CNNs and fully connected networks.  Our
results show that, for each network size, we obtain models that perform as well
or better than \textit{Static Networks}, trained via traditional hyperparameter
optimization;  (2) whether, because these  smaller networks are dense, they result in
improved inference times on both CPUs and GPUs; and (3) whether the \shrink approach results in network architectures that are
substantially different than the best network architectures (in terms of
relative number of neurons per layered) identified in the literature.

@@

We applied \shrink to the VGG16 network by adding \swls
after each \textit{BatchNorm} layer and each fully connected layer (except the
last).  Recall that \shrink assume that the starting size of the network is
an upper bound on the optimal size. Thus, we started with a
network with 2x the recommended size for each layer as an upper bound (this
is larger than what ImageNet uses). 
% Thus, for the classification
% layers we use $5000$ neurons as a starting limit.

@@

\begin{figure*}[t]\centering
\begin{minipage}{2.7in}
\centering
\includegraphics[width=\columnwidth]{CIFAR10_VGG_summary-arrows}
\vspace*{-10mm}
\caption{\label{figure_CIFAR10} Summary of the result of random
search over the hyper-parameters the \texttt{CIFAR10} dataset}
\vspace*{-5mm}
\end{minipage}
\begin{minipage}{.3in}
~~
\end{minipage}
\begin{minipage}{2.7in}
\centering\includegraphics[width=\columnwidth]{COVER_FC_summary-arrows}
\vspace*{-10mm}
\caption{\label{figure_COVER} Summary of the result of random
search over the hyper-parameters the \texttt{COVERTYPE} dataset
}
\vspace*{-5mm}
\end{minipage}
\end{figure*}

@@

\begin{figure}[htb]
\begin{center}
\includegraphics[width=.7\columnwidth]{size_evolution}
\vspace*{-5mm} 
\caption{ Evolution of the size of
  each layer over time (lighter: beginning, darker: end). On top a very large
  network performing $92.07\%$, at the bottom a simpler model with $90.5\%$
  accuracy. 
} 
\vspace*{-5mm} 
\label{fig:network_size_evolution}
\end{center}
\vspace*{-4mm}
\end{figure}

>>>>

The goal of our evaluation is to explore:

\begin{compactitem}
\item Whether, by varying $\lambda$, \shrink can efficiently
explore (in terms of number of training runs)  the spectrum of high-accuracy
models from small to large, on both CNNs and fully connected networks.  Our
results show that, for each network size, we obtain models that perform as well
or better than \textit{Static Networks}, trained via traditional hyperparameter
optimization.

\item Whether, because these  smaller networks are dense, they result in
improved inference times on both CPUs and GPUs.

\item Whether the \shrink approach results in network architectures that are
substantially different than the best network architectures (in terms of
relative number of neurons per layered) identified in the literature.

\end{compactitem}

@@

We applied \shrink to the VGG16 network by adding \swls
after each \textit{BatchNorm} layer and each fully connected layer (except the
last).  Recall that \shrink assume that the starting size of the network is
an upper bound on the optimal size. For this reason, we simply started with a
network with double the recommended size for each layer as an upper bound (this
is larger than what ImageNet, for example uses). 
% Thus, for the classification
% layers we use $5000$ neurons as a starting limit.

@@

\begin{figure*}[t]\centering
\begin{minipage}{2.7in}
\begin{center}
\includegraphics[width=\columnwidth]{CIFAR10_VGG_summary-arrows}
\vspace*{-5mm}
\caption{\label{figure_CIFAR10} Summary of the result of random
search over the hyper-parameters the \texttt{CIFAR10} dataset}
\end{center}
\vspace*{-4mm}
\end{minipage}
\begin{minipage}{2.7in}
\begin{center}
\includegraphics[width=\columnwidth]{COVER_FC_summary-arrows}
\vspace*{-5mm}
\caption{\label{figure_COVER} Summary of the result of random
search over the hyper-parameters the \texttt{COVERTYPE} dataset
\srm{label the x axes on the bottom plots; change ``Desired accuracy`` ``Accuracy''}
}
\end{center}
\vspace*{-4mm}
\end{minipage}
\end{figure*}

@@

\begin{figure}[htb]
\begin{center}
\includegraphics[width=.7\columnwidth]{size_evolution}
\vspace*{-5mm} 
\caption{ Evolution of the size of
  each layer over time (lighter: beginning, darker: end). On top a very large
  network performing $92.07\%$, at the bottom a simpler model with $90.5\%$
  accuracy. 
} 
\label{fig:network_size_evolution}
\end{center}
\vspace*{-4mm}
\end{figure}
